### 2016-05-31 capability-machine.tex
.

Assume the instructions of some adversary resides in the memory starting at the memory location marked with $\codelabel{adv}$. Assume that the register $\rio$ contains a capability for the address in memory where I/O is written to (we assume this address is 0).

@@

 Given $\Phi$, if $\memheap$ contains the ticket dispenser program starting at the address labelled $\init$, $\memreg(\pcreg) = (\rwx,\init,\init+56,\init)$, and $\Phi \rightarrow^* (\halted,\Phi')$, then the I/O address (that is $\memheap[\Phi'](0)$) contains either $-1$ or a number that is $\geq 0$ and even.

@@

The magic number 56 is the size of the above big program (minus one), so the configuration is assumed to have an execute permission for the area of the heap where the program resides.

@@

Consider what the ``good observations'' should be? Before we do that - what should the end result of a computation be?
\begin{align*}
  \observations \quad : & \quad  \Worlds \monfun \UPred{\Confs} \\%TODO: What should this be?
  \observations (W) \defeq & \{ \npair{(\reg,\heap)} \mid (\reg,\heap) \diverge \}
\end{align*}
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v\ldotp \in \stdvr(W) \Rightarrow \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat[\heap]{n'}{W'}, \npair{v_1 \dots v_k} \in \stdvr(W') \ldotp \\
                   & \qquad \quad (n,[\pcreg \mapsto \updatePcPerm{c},r_0 \mapsto v,r_1 \mapsto v_1,\dots, r_k \mapsto v_k], \heap) \in \observations(W) \}
\end{align*}

\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stder(W) \defeq & \{ \npair{\reg} \mid \\
                   & \quad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad  \forall \heapSat[\heap]{n}{W}, \heap_f \ldotp \\
                   & \qquad \quad (n,\reg\update{r_0}{c},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}

\begin{align*}
  \stdgr \quad : & \quad \Worlds \monfun \UPred{\Regs} \\
  \stdgr(W) \defeq & \{ \npair{\reg} \mid \\
                    & \quad \forall r \in \RegName \ldotp \\
                    & \qquad  \npair{\reg(r)} \in \stdvr(W) \}
\end{align*}

>>>>

Assume the instructions of some adversary resides in the memory starting at the memory location marked with $\codelabel{adv}$. Assume that the register $\rio$ initially contains a capability for the address in memory where I/O is written to (we assume this address is 0).

@@

 Given $\Phi$, if $\memheap$ contains the ticket dispenser program starting at the address labelled $\init$, $\memreg(\pcreg) = (\rwx,\init,\init+\var{proglen}-1,\init)$, $\memreg(\rio) = (\readwrite,0,0,0)$, and $\Phi \rightarrow^* (\halted,\Phi')$, then the I/O address (that is $\memheap[\Phi'](0)$) contains either $-1$ or a number that is $\geq 0$ and even.

@@

The variable $\var{proglen}$ is the length of the above program (which is about 57), so the in the initial configuration the $\pcreg$ register is assumed to have an execute and write permission for the area of the heap where the program resides.

@@

Consider what the ``good observations'' should be? Before we do that - what should the end result of a computation be?
\begin{align*}
  \observations \quad : & \quad  \Worlds \monfun \UPred{\Confs} \\%TODO: What should this be?
  \observations (W) \defeq & \{ \npair{(\reg,\heap)} \mid (\reg,\heap) \diverge \}
\end{align*}
``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v\ldotp \in \stdvr(W) \Rightarrow \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat[\heap]{n'}{W'}, \npair{v_1 \dots v_k} \in \stdvr(W') \ldotp \\
                   & \qquad \quad (n,[\pcreg \mapsto \updatePcPerm{c},r_0 \mapsto v,r_1 \mapsto v_1,\dots, r_k \mapsto v_k], \heap) \in \observations(W) \}
\end{align*}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stder(W) \defeq & \{ \npair{\reg} \mid \\
                   & \quad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad  \forall \heapSat[\heap]{n}{W}, \heap_f \ldotp \\
                   & \qquad \quad (n,\reg\update{r_0}{c},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}
Register-file relation:
\begin{align*}
  \stdgr \quad : & \quad \Worlds \monfun \UPred{\Regs} \\
  \stdgr(W) \defeq & \{ \npair{\reg} \mid \\
                    & \quad \forall r \in \RegName \ldotp \\
                    & \qquad  \npair{\reg(r)} \in \stdvr(W) \}
\end{align*}
